---
title: "eqv vignittes"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

#Package eqv allows clean up & visualization of the NOAA earthquake dataset.  The document describes some of the functionalities available in the eqv package.
## In the example below, we will see the use of the following functions from the eqv package:
### eq_clean_data()
### eq_location_data()
### geom_timeline()
### geom_timeline_label()

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(eqv)
library(dplyr)
library(ggplot2)
library(readr)
filename <- system.file("extdata/signif.txt", package = "eqv")
data <- readr::read_delim(filename, delim = "\t")
data %>%
  eq_clean_data() %>%
  eq_location_clean %>%
  dplyr::filter(COUNTRY %in% c("INDIA", "ITALY") & YEAR > 1990) %>%
  ggplot2::ggplot(ggplot2::aes(x  = DATE, y = COUNTRY,color = as.numeric(TOTAL_DEATHS),size = as.numeric(EQ_PRIMARY))) + 
  geom_timeline() + 
  geom_timeline_label(ggplot2::aes(label = LOCATION_NAME), n_max = 5) + 
  theme_timeline()

```

## Example below shows use of the following functions that can be used with leaflet package functions.
### eq_create_label()
### eq_map()


```{r, echo=FALSE, message=FALSE, warning=FALSE}
data %>% 
  eq_clean_data() %>% 
  dplyr::filter(COUNTRY == "MEXICO" & lubridate::year(DATE) >= 2000) %>% 
  dplyr::mutate(popup_text = eq_create_label(.)) %>% 
  eq_map(annot_col = "popup_text")
```
